\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\topmargin=-45pt  
\headheight=12truept 
\headsep=25pt
\footskip=37pt 
\hoffset=0pt 
\voffset=12pt
\oddsidemargin=0cm 
\evensidemargin=0cm
\textheight=23.7cm 
\textwidth=16.0cm

\def \nequiv {\equiv \hspace{-3mm} / \hspace{1mm}}
\def \qed {\hfill \hbox {\rule [-2pt]{3pt}{6pt}}}
%\pagestyle{myheadings}
%%%%%%%%%%%%%
\newtheorem{thm}{Theorem}%[chapter]% THEOREM
\newtheorem{theorem}[thm]{Theorem}
\newtheorem{prop}[thm]{Proposition}% PROPOSITION
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}% COROLLARY
\newtheorem{corollary}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}% LEMMA
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{remark}[thm]{Remark}
\newtheorem{defi}[thm]{Definition}
\newtheorem{definition}[thm]{Definition}
%\newtheorem{example}[thm]{Example}

\begin{document}
\title{Optimal Execution Strategies Incorporating Internal Liquidity Through Market Making}

\author{
Yusuke MORIMOTO
\thanks{
MUFG Bank, Ltd, 1-4-5 Marunouchi, Chiyoda-ku, Tokyo 100-8388, Japan, \
E-mail: yuusuke.morimoto@gmail.com} }
\date{}
\maketitle
\begin{abstract}
This paper proposes a novel algorithmic execution model that integrates interbank limit and market orders with internal liquidity provided through market making. 
Building upon a widely used framework for optimal execution, the model incorporates market impact for interbank orders while excluding it for internal market-making executions. The objective is to optimize the allocation between interbank and internal liquidity, thereby reducing market impact and enhancing execution efficiency.
\end{abstract}

JEL Classification: C41, G11
Mathematical Subject Classification (2010): 65C05, 60G40
Keywords: Algorithmic Trading, Market Impact, Optimal Execution, Liquidation, Stochastic Control, Impulse Control

\section*{Declarations}

\textbf{Author Contributions:} The author conducted all theoretical modeling, data analysis, and manuscript preparation.

\textbf{Acknowledgments:}  The author would like to thank Dr. Keiichi Maeta of MUFG Bank for insightful discussions, and Mr. Katsumi Takada of Diva Analytics for his valuable comments.


\textbf{Funding:} The author received no financial support for this research.

\textbf{Conflicts of Interest:} The author declares no conflicts of interest.


\end{document}


