Specific comments (not exhaustive)
P1 L40-44: The sentence beginning with "Algorithmic...." is excessively long and difficult to follow. It would be clearer and more readable if divided into several shorter sentences.
P2 L14-L16: The two sentences ``There has been ... markers." continue with "All of which..." by mistake.
P2 L16: At first glance, "This paper" is confusing with one of [2], [11] and [4]. ``The present work'' would suit better.
P2 L26: "the Cartea et al. [6] framework" is too rough.
P2 L30: liquidities?
P2 L36-37: Section 2 does not cite any existing literature. Does its content represent the novel contribution of the submitted manuscript?
P2 L40: "both as market makers and takers" grammar???
P3 L55: "In this section, .... for more rigorous proofs." I don't understand this sentence at all. Since no proof is presented in this section, what exactly do you mean by "more proofs"?
P4 L10: Y_t or Y(t)?
P4 L22-L26: These two equation displays appear all of sudden. Do these stand alone?
P4 L52-: These items appear abruptly without any introductory sentence. What exactly are you intending to present by listing them in this way?
P5 L39: Following ".... as follows." (which is a completed sentence at the moment), three equation displays begin. Are those three equation displays regarded as a sentence???
P5 L55: "represent"???
P5 L59: What do you mean by "to be a linear of"???
P5 L61: What do you mean by "This is analogous that...."???
P6 L7: "into" in place of "for"??? What does "them" refer to?
P6 L12: "indicates" in place of "shows"???
P6 L18: "represents" grammar???
P6 L26-29: This A(s,y) was defined in P4.
P6 L35: "a" composed expectation???
P6 L39: "indicates" in place of "represents"???
P6 L44: "represents" in place of "shows"???
Sections 3.3 and 3.4 are presented too abruptly. That is, no derivations or references are provided. Do these sections represent the original contribution of the present work?
P7 L5: "are corresponding to"???
P8 L42-44: "it can be computed numerically .... method" No references? Is this a finding of the present work???
P8 L44: "the the"???
P10 L52: Why is there a closing double quotation mark here? There doesn't appear to be any corresponding quotation.
P11 L14-18: I wonder if this single sentence is to be taken as a comprehensive conclusion of the paper???
There is additional documentation related to this decision letter. To access the file(s), please click the link below. You may also login to the system and click the 'View Attachments' link in the Action column.